Functional Enrichment Tests: Intro and methods comparison

### 2023-07-14 DRAFT_Funct_Enrich.Rmd
rearranged some text, changed header name, added description in getting to enrichment analysis section

# Overview

@@

Finding your subset of genes of interest

-   Differential expression
-   Clustering
-   WGCNA

>>>>

# Considerations for a Rigourous Analysis

@@

Once the challenge of annotating data has been met, the next step is determining the focus of your functional analysis. In some cases, you will use the complete dataset, but in other cases you may be interested in a subset of interest. There are numerous approaches that can be used to achieve this, many with excellent tutorials available online. These include:

-   Differential Expression Analysis
-   Clustering
-   WGCNA
